---
title: "Buisiness Analysis Project of IKEA FURNITURE"
author: "Rachelxiong s4647301 & Sammi Ma s4659396"
date: "9/14/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data
```{r}
library(tidyverse)
library(knitr)
library(tidymodels)
library(patchwork)
ikea <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-11-03/ikea.csv')
summary(ikea)
```

---
## DATA CLEANSING
Before we start our data analysis, there are some cleaning to be done in this dataset.
### 1. Unified the currency
```{r}
ikea%>%mutate(price_usd = round(price * 0.27, 1))
```
### 2. Calculate the volume of each iteam.
```{r}
na_volume <- ikea %>%
  na.omit(depth) %>%
  na.omit(height) %>%
  na.omit(width) %>%
  mutate(volume_m3 = height * width * depth / (100^3))
```

### 3. How many items have other color?
```{r}
ikea%>%
  mutate(price_usd = round(price * 0.27, 1))%>%
  filter(other_colors == 'Yes')%>%
  count(price_usd)
```

## ASKING QUESTIONS
### Major question: Can we predict the price of the IKEA furniture by knowing their categories and colour?
Subquestions:
Q1. What's the average price of IKEA furniture per category?
Q2. What is the relation between the price and the colour?
Q3. Is the relation between the price and category  dependent on volume?

## DESCRIPTIVE or EXPLORATORY ANALYSIS
Now let's explore the data by finding the answer to the above subquestions.

### 1. What's the average price of IKEA furniture per category?
```{r}
ikea%>%
  group_by(category)%>%
  mutate(price_usd = round(price * 0.27, 1))%>%
  summarise(count=n(),average_price=mean(price_usd))%>%
  ggplot(aes(x = category, y = average_price)) +
  geom_col() + 
  coord_flip() +
  theme_minimal() +
  labs(x = "Category",
       y = "Average price",
       title = "What's the average price of IKEA furniture per category")

```

### 2. What is the relation between the price and color?
```{r}
na_volume %>%
  mutate(price_usd = round(price * 0.27, 1))%>%
  filter(other_colors =="Yes") %>%
  count(price_usd) %>%
  ggplot(aes(price_usd,n))+geom_point(fill="blue")+
  geom_smooth(method = lm, se = FALSE)+labs(title='The price_usd distribution of items which have other colors')
```

### 3. What is the relation between the price and volume?
```{r}
na_volume %>%
  ggplot(aes(price, volume_m3)) +
  geom_point() +
  geom_smooth(method = lm, se = FALSE) +
  scale_color_viridis_d(option = "plasma", end = .7) +
  labs(x = "price", y = "volume", colour = "cetegory", title = "")


```





